Market Simulator

### 2020-07-23 analysis/05_market_simulator.Rmd
Updated some information and changed layout

---
title: "Data Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

##### Updated the beta's to be just the betas from the public_political_social_charity_demo Thetas

@@

Practice
-------------------------------------------------------
```{r practice code}

@@

Inputs {.sidebar}
-------------------------------------------------------

@@

@@

Row
-------------------------------------

@@

Row 
-------------------------------------
### Amnesty International Expected Utility

@@

### Greenpeace Expected Utility

@@

### Oxfam Expected Utility

@@

### Redcross Expected Utility

@@

Row 
-------------------------------------

### Amnesty International Expected Donors

@@

Row 
-------------------------------------

### Amnesty International Inputs

>>>>

---
title: "Market Simulator"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

@@

@@

```{r practice code}

@@

Inputs {.sidebar data-width=50}
-------------------------------------------------------

@@

``` {r echo=FALSE}

@@

Market Share and Expected Utility
--------------------------------------------------

@@

Organization Utility
-------------------------------------
Amnesty International Expected Utility

@@

## Greenpeace Expected Utility

@@

## Oxfam Expected Utility

@@

## Redcross Expected Utility

@@

Expected Donors {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Expected Donors

@@

Organizational Inputs {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Inputs
